title: "US GAS Demand"
date: "2026-05-05"
output: html_document
---



```{r}
install.packages("EIAapi")
install.packages("tidyverse")
install.packages("ggplot2")
library(EIAapi)
library(tidyverse)
library(ggplot2)
library(httr)
library(jsonlite)
```
```
```{r}
## Setting up the paramters for the api including the key and the path, from eia.gov/opendata

api_key  <- "XH6BAfw0jn83wuor37ggwPEA98TEDhX58hDlBMWD"
api_path <- "gas/cons/sum/data/"

```


```{r}
# Setting up the frequency and dates - between july 2023 and february 2026

frequency <- "monthly"
start_date <- "2023-07"
end_date   <- "2026-02"


# 2. Separated Date Variables (July 2023 to Feb 2026)
start_val <- "2023-07"
end_val   <- "2026-02"

url <- paste0(
  "https://api.eia.gov/v2/", api_path, 
  "/?api_key=", api_key,
  "&frequency=monthly",
  "&data[0]=value",
  "&facets[process][]=VGT", # Delivered to Consumers
  "&facets[process][]=VIN", # Industrial
  "&facets[process][]=VRS", # Residential
  "&start=", start_val,
  "&end=", end_val,
  "&sort[0][column]=period",
  "&sort[0][direction]=desc",
  "&offset=0",
  "&length=5000"
)

#Pulling the response using get
response <- GET(url)

#Parse the JSON content

json_content <- fromJSON(content(response, as = "text", encoding = "UTF-8"))


#Extract the data frame, since the dataframe is pulled - November 2021 to June 2023
df_ng_demand_1 <- json_content$response$data

print(head(df_ng_demand_1 ))


# Saving as csv
write.csv(df_ng_demand_1, file = "df_ng_demand_1.csv")


```


```{r}
## Parameters changed between november 2021 to june 2023

frequency <- "monthly"
start_date <- "2021-11"
end_date   <- "2023-06"

# URL for the api, we need to include the api key here, maximum length for each query is 5000

url <- paste0(
  "https://api.eia.gov/v2/", api_path, 
  "/?api_key=", api_key,
  "&frequency=monthly&data[0]=value",
  "&start=", start_date,   
  "&end=", end_date, 
  "&facets[process][]=PEU&facets[process][]=PIN&facets[process][]=PRS",
  "&sort[0][column]=period&sort[0][direction]=desc&length=5000"
)
#Pulling the response using get
response <- GET(url)

#Parse the JSON content

json_content <- fromJSON(content(response, as = "text", encoding = "UTF-8"))


#Extract the data frame, since the dataframe is pulled - November 2021 to June 2023
df_ng_2 <- json_content$response$data
  
print(head(df_ng_2 ))


# Saving as csv
write.csv(df_ng_2, file = "df_ng_2.csv")
```

