title: "US GAS Prices"
date: "2026-05-05"
output: html_document
---



```{r}
install.packages("EIAapi")
install.packages("tidyverse")
install.packages("ggplot2")
library(EIAapi)
library(tidyverse)
library(ggplot2)
library(httr)
library(jsonlite)
```
```
```{r}
## Setting up the paramters for the api including the key and the path, from eia.gov/opendata

api_key  <- "XH6BAfw0jn83wuor37ggwPEA98TEDhX58hDlBMWD"
api_path <- "electricity/retail-sales/data/"

```


## Commercial Prices

```{r}
# Setting up the frequency and dates for commercial prices

frequency <- "monthly"
start_date <- "2021-11"
end_date   <- "2026-02"


# URL for the api, we need to include the api key here, maximum length for each query is 5000

url <- paste0(
  "https://api.eia.gov/v2/", api_path, 
  "/?api_key=", api_key,
  "&frequency=monthly&data[0]=price",
  "&start=", start_date,   
  "&end=", end_date, 
  "&facets[sectorid][]=COM&",
  "&sort[0][column]=period&sort[0][direction]=desc&length=5000")


#Pulling the response using get
response <- GET(url)


#Parse the JSON content

json_content <- fromJSON(content(response, as = "text", encoding = "UTF-8"))


#Extract the data frame
df_ep_com <- json_content$response$data
  
print(head(df_ep_com ))

# Saving as csv
write.csv(df_ep_com, file = "df_ep_com.csv")

```

#Industrial Prices

```{r}
# Setting up the frequency and dates for industrial prices

frequency <- "monthly"
start_date <- "2021-11"
end_date   <- "2026-02"


# URL for the api, we need to include the api key here, maximum length for each query is 5000

url <- paste0(
  "https://api.eia.gov/v2/", api_path, 
  "/?api_key=", api_key,
  "&frequency=monthly&data[0]=price",
  "&start=", start_date,   
  "&end=", end_date, 
  "&facets[sectorid][]=IND&",
  "&sort[0][column]=period&sort[0][direction]=desc&length=5000")


#Pulling the response using get
response <- GET(url)


#Parse the JSON content

json_content <- fromJSON(content(response, as = "text", encoding = "UTF-8"))


#Extract the data frame
df_ep_ind <- json_content$response$data
  
print(head(df_ep_ind))

# Saving as csv
write.csv(df_ep_ind, file = "df_ep_ind.csv")
```



#Residential

```{r}
# Setting up the frequency and dates for residential prices

frequency <- "monthly"
start_date <- "2021-11"
end_date   <- "2026-02"


# URL for the api, we need to include the api key here, maximum length for each query is 5000

url <- paste0(
  "https://api.eia.gov/v2/", api_path, 
  "/?api_key=", api_key,
  "&frequency=monthly&data[0]=price",
  "&start=", start_date,   
  "&end=", end_date, 
  "&facets[sectorid][]=RES&",
  "&sort[0][column]=period&sort[0][direction]=desc&length=5000")


#Pulling the response using get
response <- GET(url)


#Parse the JSON content

json_content <- fromJSON(content(response, as = "text", encoding = "UTF-8"))


#Extract the data frame, since the dataframe is pulled from - July 2023 - Feb 2026
df_ep_res <- json_content$response$data
  
print(head(df_ep_res))

# Saving as csv
write.csv(df_ep_ind, file = "df_ep_res.csv")
```


#Transportation


```{r}
# Setting up the frequency and dates for transportation prices

frequency <- "monthly"
start_date <- "2021-11"
end_date   <- "2026-02"


# URL for the api, we need to include the api key here, maximum length for each query is 5000

url <- paste0(
  "https://api.eia.gov/v2/", api_path, 
  "/?api_key=", api_key,
  "&frequency=monthly&data[0]=price",
  "&start=", start_date,   
  "&end=", end_date, 
  "&facets[sectorid][]=TRA&",
  "&sort[0][column]=period&sort[0][direction]=desc&length=5000")


#Pulling the response using get
response <- GET(url)


#Parse the JSON content

json_content <- fromJSON(content(response, as = "text", encoding = "UTF-8"))


#Extract the data frame, since the dataframe is pulled from - July 2023 - Feb 2026
df_ep_tra <- json_content$response$data
  
print(head(df_ep_res))

# Saving as csv
write.csv(df_ep_tra, file = "df_ep_tra.csv")
```





